POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-04-26 main.tex
some rework

This section is not (at least initially) meant to be in the final
manuscript but it is to document some reasoning for choosing
appropriate problems. The idea is to explore three areas: scope
extrusion in name passing calculi, linearity requirements in
behavioural types, and finally coinductive reasoning in trace
equivalence, (bi)similarity, or subtyping in the presence of
recursion.

@@

But the exact presentation of the concrete problems should be somewhat
flexible. In the sense that the use of certain techniques or tools may
require changing the presentation of the system to fit the technique.
These changes should be allowed, and even encouraged, but the result
should be ``morally'' the same system and there should be a
rationale for the changes in presentation. That way we could not only
see valid techniques but also what presentation of the rules to use
and the rationale to chose a particular approach.

>>>>

 The idea is to explore three areas: scope
extrusion in name passing calculi, linearity requirements in
behavioural types, and finally coinductive reasoning in trace
equivalence, (bi)similarity, or subtyping in the presence of
recursion.

@@

But the exact presentation of the concrete problems is somewhat
flexible. In the sense that the use of certain techniques or tools may
require changing the presentation of the system to fit the technique.
We are more interested in the techniques that are applicable to these
problems as a class of problems than to the exact specification we
propose. Of course, for clarity if a solution changes the definition
it should document in what sense the definition differs. So changes
allowed, and even encouraged, but the result should be ``morally'' the
same system and there should be a rationale for the changes in
presentation. That way we not only see valid techniques but also what
presentation of the rules to use and the rationale to chose a
particular approach.
